Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-06-13 2020/OPTIMA/optima_paper.tex
check all paper

\begin{theorem} (On convergence conditions) Let the conditions of the Theorem \ref{th:single_conv}
  are satisfied for all of \(q\) problems from the set (\ref{eq:many_problems}) separately.
  Then solving all of the \(q\) problems by the algorithm from Section \ref{sec:method} will
  generate \(q\) infinite sequences, for the limit points of which the Theorem \ref{th:single_conv}
  will be also true.
\end{theorem}
\begin{proof}
  Let us consider two random problems from the set \ref{eq:many_problems}.
  \begin{equation}
      \begin{array}{lr}
        \min\{\varphi(y):y\in D_1,\: g_j^\varphi(y)\leqslant 0, 1\leqslant j\leqslant m_1\} \\
        \min\{\psi(y):y\in D_2,\: g_j^\psi(y)\leqslant 0, 1\leqslant j\leqslant m_2\}
      \end{array}
  \end{equation}
  Let us denote the characteristics (\ref{step3_1}) for the first problem as \(R_\varphi(i)\)
  and for the second problem as \(R_\psi(j)\). Considering that, we have:
  \begin{equation}
      \begin{array}{lr}
        R_\varphi(t_\varphi)=\max_{1\leqslant i\leqslant k}R_\varphi(i), \\
        R_\psi(t_\psi)=\max_{1\leqslant j\leqslant s}R_\psi(j),
      \end{array}
  \end{equation}
  where \(k\) corresponds to the number of trials in the first problem and \(s\)
  corresponds to the number of trials in the second one. The sequence of trials \(\{v^k\}\)
  corresponds to the first problem and the sequence of trials \(\{u^s\}\)
  corresponds to the second problem. The values \(z^k=g^\varphi_\nu(v_k),\nu =\nu (v_{k})\) correspond to the
  trial points \(\{v^k\}\) and the values \(w^s=g^\psi_\nu(u_s),\nu =\nu(u_{s})\) correspond to the
  trial points \(\{u^s\}\).

@@

  Let us consider the first case: from (\ref{step2})
  \begin{displaymath}
    \frac{|z_i-z_{i-1}|}{\Delta_i} \leqslant \mu_{\varphi,\nu}.
  \end{displaymath}
  Considering that, we can establish an upper bound:
  \begin{displaymath}
    \frac{(z_i-z_{i-1})^2}{r_\nu^2\mu_{\varphi,\nu}^2\Delta_i}=\frac{(z_i-z_{i-1})^2\Delta_i}{(r_\nu\mu_{\varphi,\nu}\Delta_i)^2}
    \leqslant \frac{\Delta_i}{r_\nu^2}.
  \end{displaymath}
  Therefore using the first branch form rule (\ref{step3_1}) we have inequality
  \begin{equation}
    \label{eq:th1}
    R_\varphi(i)\leqslant\Delta_i(1 + \frac{1}{r_\nu^2}) - \frac{2(z_i+z_{i-1}-2z^*_\nu)}{r_\nu\mu_{\varphi,\nu}}.
  \end{equation}
  Because \(\overline{v}\) is the limit point of the sequence \(\{v^k\}\) and \(\varphi(y(\overline{v}))\leqslant z^*_{\nu}, \nu=m+1\) or
  \(z^*_\nu=0, \nu<m+1\) and \(z_{i-1},z_i\to 0\) at \(k\to\infty\):
  \begin{equation}
    \label{eq:th2}
    \Delta_i\to 0, z_i+z_{i-1} - 2 z_\nu^*\to 0.
  \end{equation}
  In the second case (when one of the other two branches rule (\ref{step3_1}) is applied) from we have
  \begin{displaymath}
    R_\varphi(i)=2\Delta_i + 4\frac{z^*_\nu-z_i}{r_\nu\mu_{\varphi,\nu}}
  \end{displaymath}
  If \(z^*_\nu \ne 0\) then \(z_i-z^*_\nu \geqslant 0\) and
  \begin{equation}
    \label{eq:th3}
    R_\varphi(i)=2\Delta_i - 4\frac{z_i-z^*_\nu}{r_\nu\mu_{\varphi,\nu}} \leqslant 2\Delta_i.
  \end{equation}
  Otherwise because of \(\overline{v}\) is feasible point \(z_i\to 0\) at \(k\to\infty\).

>>>>

\begin{theorem} (On convergence conditions) Let the conditions of the Theorem \ref{th:single_conv}
  are satisfied for all of \(q\) problems from the set (\ref{eq:many_problems}) separately.
  Then solving all of the \(q\) problems by the algorithm from Section \ref{sec:method} will
  generate \(q\) infinite sequences, for the limit points of which the Theorem \ref{th:single_conv}
  will be also true.
\end{theorem}
\begin{proof}
  Let us consider two random problems from the set (\ref{eq:many_problems}).
  \begin{equation}
      \begin{array}{lr}
        \min\{\varphi(y):y\in D_1,\: g_j^\varphi(y)\leqslant 0, 1\leqslant j\leqslant m_1\} \\
        \min\{\psi(y):y\in D_2,\: g_j^\psi(y)\leqslant 0, 1\leqslant j\leqslant m_2\}
      \end{array}
  \end{equation}
  Let us denote the characteristics (\ref{step3_1}) for the first problem as \(R_\varphi(i)\)
  and for the second problem as \(R_\psi(j)\). Considering that, we have:
  \begin{equation}
      \begin{array}{lr}
        R_\varphi(t_\varphi)=\max_{1\leqslant i\leqslant k}R_\varphi(i), \\
        R_\psi(t_\psi)=\max_{1\leqslant j\leqslant s}R_\psi(j),
      \end{array}
  \end{equation}
  where \(k\) corresponds to the number of trials in the first problem and \(s\)
  corresponds to the number of trials in the second one. The sequence of trials \(\{v^k\}\)
  corresponds to the first problem and the sequence of trials \(\{u^s\}\)
  corresponds to the second problem. The values \(z^k=g^\varphi_\nu(v_k),\nu =\nu (v_{k})\) correspond to the
  trial points \(\{v^k\}\) and the values \(w^s=g^\psi_\nu(u_s),\nu =\nu(u_{s})\) correspond to the
  trial points \(\{u^s\}\).

@@

  Let us consider the first case: from (\ref{step2})
  \begin{displaymath}
    \frac{|z_i-z_{i-1}|}{\Delta_i} \leqslant \mu_{\varphi,\nu}.
  \end{displaymath}
  Considering that, we can establish an upper bound:
  \begin{displaymath}
    \frac{(z_i-z_{i-1})^2}{r_\nu^2\mu_{\varphi,\nu}^2\Delta_i}=\frac{(z_i-z_{i-1})^2\Delta_i}{(r_\nu\mu_{\varphi,\nu}\Delta_i)^2}
    \leqslant \frac{\Delta_i}{r_\nu^2}.
  \end{displaymath}
  Therefore using the first branch form rule (\ref{step3_1}) we have inequality
  \begin{equation}
    \label{eq:th1}
    R_\varphi(i)\leqslant\Delta_i(1 + \frac{1}{r_\nu^2}) - \frac{2(z_i+z_{i-1}-2z^*_\nu)}{r_\nu\mu_{\varphi,\nu}}.
  \end{equation}
  Because \(\overline{v}\) is the limit point of the sequence \(\{v^k\}\) and \(\varphi(y(\overline{v}))\leqslant z^*_{\nu}, \nu=m+1\) or
  \(z^*_\nu=0, \nu<m+1\) and \(z_{i-1},z_i\to 0\) at \(k\to\infty\):
  \begin{equation}
    \label{eq:th2}
    \Delta_i\to 0, z_i+z_{i-1} - 2 z_\nu^*\to 0.
  \end{equation}
  In the second case (when one of the other two branches of the rule (\ref{step3_1}) is applied) we have
  \begin{displaymath}
    R_\varphi(i)=2\Delta_i - 4\frac{z_i-z^*_\nu}{r_\nu\mu_{\varphi,\nu}}
  \end{displaymath}
  If \(z^*_\nu \ne 0\) then \(z_i-z^*_\nu \geqslant 0\) and
  \begin{equation}
    \label{eq:th3}
    R_\varphi(i)=2\Delta_i - 4\frac{z_i-z^*_\nu}{r_\nu\mu_{\varphi,\nu}} \leqslant 2\Delta_i.
  \end{equation}
  Otherwise because of \(\overline{v}\) is a feasible point \(z_i\to 0\) at \(k\to\infty\).
